---
title: "Brownlows Bets"
author: "Gracie Telles"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)
source(file="BrLw.R")
```



# Introduction


 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 637 times so far. Where do you think his profits are? 
 
1. What are the fair odds for a bet on matching birthdays in a 35 person class.

2. For what size class is a 2:1 odds bet fair?

3. How much money would Brownlow be expected to end up with if the bets went as described.

## Our strategy is to build a Function and the use it to answer the three questions. 

#In the class and payoff as described  If you hired 40 Brownlow substitute teachers to do the same thing that Brownlow did then.
#What is their average earnings
#The standard deviation and a 95% confidence interval for their earnings?
  

# What are the fair odds? 

```{r}
money=BrLw(35,4.4,637)
print (money)
```

Fair odds would be 4.4 for the odds.


# What size of class makes the 2:1 bet fair?  

```{r}
money=BrLw(28,2,637)
print(money)
```

To make the payoffs fair there would have to be 28 students.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->

